\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

The writing and completion of this dissertation would not have been possible without the assistance, support, and guidance of the many special people in my life. Firstly, I would like to thank God for giving me the capability to contribute to the engineering world and hopefully assist the future civilizations in creating technologies for the good of mankind. Technology has been abused by the powers that be, and I hope that, someday, ethical values will be the priorities of our future leaders in order to sustain peace and harmony in this planet. 

Secondly, I would like to thank my EPFL advisor, Dr. Alireza Karimi. 
I have learned many things from him since starting my Ph.D, and I thank him for accepting me into his program. His contributions and patience were key factors in the successful completion of this dissertation.
I would also like to thank my CERN supervisor, Dr. Michele Martino. 
He has been very helpful during my Ph.D studies, and I have enjoyed the numerous technical discussions I had with him; I always learned something from each discussion, and am very appreciative for that. 
Among my other CERN colleagues, I would like to also thank Miguel Cerqueira Bastos, Quentin King, Olivier Michele, Davide Aguglia, Todor Todorvic, Ivan Jovetic, Olivier Founier, and Louis De Mallac. 
The knowledge that I have acquired from Michele and my numerous colleagues will be something that I will foster and cherish for the rest of my life.

In addition to my work colleagues, I would also like to thank Zlatko Emedji and Jose Manuel De Paco Soto for being good friends and providing the emotional support I needed. Also a thank you to Predrag Milosavljevic and Christoph Kammer for being good competitors at Foosball during my time at EPFL. Additionally, I would like to thank Michael Davis, Hugo Lebreton, Miguel Hermo Serans, and Timm Faulwasser for our random technical and non-technical discussions. 


Finally, I would like to thank my family for their support during this endeavour. 
My sisters Carmen, Marie, and Elizabeth have been great inspirations to me; they shaped me into the person I am today and can honestly say that without them, I may not have been so successful. 
To my mother, I thank you for everything you have done for me during my 33 years on this planet. 
I will always carry your love in my heart. 
And finally, to my father, I wish you could have still been with us to witness this moment in my life. 
I know that you would have been proud of me, and am very grateful for all of the sacrifices you made for the family.


\bigskip
 
\noindent\textit{Geneva, 12 March 2017}
\hfill A.~N.
